%\documentclass[handout]{beamer}
\documentclass[evncountsect]{beamer}
\usepackage{amsmath,algorithm,algorithmic,graphicx,amsfonts,amsthm,color,pgf,tikz,wrapfig,amsfonts,multicol,wasysym,animate}
\usepackage[absolute,overlay]{textpos}
\usetikzlibrary{arrows}
\beamertemplatenavigationsymbolsempty
\setbeamercovered{transparent = 0}
\useoutertheme[subsection=false]{miniframes}
\bibliographystyle{apalike}
\setlength{\fboxrule}{1pt}

\title{RNA-seq and Adaptive Shrinkage}
\author{David Gerard and Mengyin Lu}
\institute[UChicago]{
  Department of Human Genetics\\
  University of Chicago\\
  Boss: Matthew Stephens
}
\date[September 2016]{September, 2016}

% available at https://github.com/matze/mtheme
\usetheme{metropolis}

\begin{document}


\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{RNA-seq}
  What is RNA-seq?
  \begin{enumerate}
  \item Each cell in our body contains a population of RNA fragments. \medskip
  \item These RNA fragments are the output (``expression'') of genes.\medskip
  \item RNA-seq uses next-gen sequencing to measure the relative
    expression of genes within a sample.\medskip
  \item Relative differences in the expression levels of these RNA
    fragments between groups tell us interesting things:
    \begin{enumerate}
    \item Which genes are influenced by a drug?\smallskip
    \item How do cancer patients differ from non-cancer patients?\smallskip
    \item Which genes are important in liver tissue versus muscle tissue?
    \end{enumerate}
  \end{enumerate}

  % Improvements over older technology:
  % \begin{enumerate}
  % \item Do not need prior knowledge of a gene to measure its expression level.
  % \item Can compare genes within a sample.
  % \item More accurate measurements of low/high expressed genes.
  % \end{enumerate}
\end{frame}


\begin{frame}{Many Problems}
  \begin{enumerate}
  \item Count Data: A new type of data that requires new normalization
    procedures/pipelines.\medskip
  \item Small Sample Sizes: Low power. Hard to detect differences between groups.\medskip
  \item Unobserved Variables: Can ruin analyses. Can make results uninterpretable.
    \begin{enumerate}
    \item Which lab/technician processed a sample?\smallskip
    \item The ancestry of the sample.\smallskip
    \item Subject attributes such as age or sex.
    \end{enumerate}
  \end{enumerate}
\end{frame}

\begin{frame}{Our Work}
  \begin{enumerate}
  \item Count Data: Develop optimal pipelines for analysis.
    \begin{enumerate}
    \item Which published methods work in practice?\smallskip
    \item Develop benchmarks to compare pipelines.\medskip
    \end{enumerate}
  \item Small Sample Sizes:
    \begin{enumerate}
    \item Harness the power of ASH.\smallskip
    \item Borrow strength between variables.
    \end{enumerate}\medskip
  \item Unobserved Variables:
    \begin{enumerate}
    \item Integrate ``factor-augmented regression'' models with the
      shrinkage ideas from ASH. \smallskip
    \item Modify known approaches to optimize the performance of ASH.
    \end{enumerate}
  \end{enumerate}
\end{frame}

\end{document}